\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------



\begin{document}



\begin{center}
\textbf{\Huge \scshape Ansh Gupta} \\ \vspace{1pt}
\small +91-9369143625 $|$ \href{mailto:anshtechnical@gmail.com}{\underline{anshtechnical@gmail.com}} $|$ 
\href{https://linkedin.com/in/techbire}{\underline{linkedin.com/in/techbire}} $|$
\href{https://github.com/techbire}{\underline{github.com/techbire}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Lovely Professional University}{Phagwara, Punjab}
{Bachelor of Technology in Computer Science}{Aug. 2023 -- May 2027}
\resumeSubheading
{Manasthali Education Centre}{Ballia, Uttar Pradesh}
{Higher Secondary Education }{Aug. 2021 -- May 2023}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineering Fellow}{July 2024 -- Sept 2024}
{Headstarter}{Remote}
\resumeItemListStart
\resumeItem{Developed AI-driven applications within 7 weeks, achieving \textbf{\href{https://www.linkedin.com/posts/techbire_ai-machinelearning-webdev-activity-7232788721408884736-oU2e?utm_source=share&utm_medium=member_desktop}{top 1\%}} ranking on the fellowship leaderboard.}
\resumeItem{Utilized agile method with weekly sprints and CI/CD practices to ensure timely and efficient project delivery.}
\resumeItem{Built a dynamic flashcard SaaS product using Gemini LLM and integrating Stripe for paywall and custom pricing plans, leading to a 30\% increase in user retention.}

\resumeItemListEnd


%     \resumeSubheading
%       {Content Writer}{June 2020 -- March 2021}
%       {Dailyhunt}{Remote}
%       \resumeItemListStart
% \resumeItem{Utilized social media and platform tools to enhance blog reach and visibility, collaborating with industry professionals.}
% \resumeItem{Authored engaging tech content, amassing over 7000 followers within 4 months.}
%       \resumeItemListEnd

% %-------------------------------------------

%     \resumeSubheading
%       {Founder}{Nov. 2017 -- May 2020}
%       {TechBire}{Remote}
%       \resumeItemListStart
% \resumeItem{Founded and grew a successful tech blog, achieving Google AdSense approval transitioning the blog to a monetized platform.}
% \resumeItem{Created high-impact tech content and implemented SEO strategies to secure top search positions.}
%     \resumeItemListEnd

%-----------PROJECTS-----------
\section{Projects}

\resumeProjectHeading
{\textbf{Flashcard SaaS} $|$ \emph{Next.js, Gemini LLM, Clerk, Firebase, Netlify} \textbf{\hfill \href{https://github.com/techbire/flashcard-saas}{Demo Link}}}{Aug. 2024 -- Aug. 2024}
\resumeItemListStart
\resumeItem{Developed a web application for generating, managing, and reviewing flashcards, leveraging Gemini LLM for AI-powered flashcard generation and Firebase for secure data storage.}
\resumeItem{Integrated user authentication with Clerk, enabling users to save and access their flashcard collections.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Pantry Tracker} $|$ \emph{Next.js, Firebase, Vercel} \textbf{\hfill \href{https://github.com/techbire/pantry-tracker}{Demo Link}}}{July 2024 -- Aug. 2024}
\resumeItemListStart
\resumeItem{Created a web application to manage pantry items, featuring expiration alerts, inventory management, and a shopping list. Implemented real-time updates for inventory changes.}
\resumeItem{Implemented Firebase Firestore for real-time data synchronization across devices.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{TechBire AI} $|$ \emph{Gemini LLM, Python, Streamlit} \textbf{\hfill \href{https://github.com/techbire/techbire-AI}{Demo Link}}}{March 2024 -- May 2024}
\resumeItemListStart
\resumeItem{Built a Streamlit application utilizing Google's Gemini LLM to generate responses to user queries with context retention for detailed interactions.}
\resumeItem{Integrated an interactive chat interface that includes a history feature for reviewing past conversations.}
\resumeItem{Provided formatted code snippets in multiple programming languages to assist users with programming queries.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Bharat Trade} $|$ \emph{C, Python} \textbf{\hfill \href{https://github.com/techbire/bharat-trade}{Demo Link}}}{April 2024 -- May 2024}
\resumeItemListStart
\resumeItem{Implemented a command-line stock trading simulator in C and Python, enabling actions like adding money, investing, and viewing balances.}
\resumeItem{Incorporated real-time stock data retrieval using the `yfinance` library in Python.}
\resumeItem{Utilized file handling functionalities for storing stock data and account information.}
\resumeItemListEnd


% \resumeProjectHeading
% {\textbf{KBC: The Quiz Game} $|$ \emph{Python, Pygame}}{Nov. 2023 -- Dec 2023}
% \resumeItemListStart
% \resumeItem{Developed an interactive quiz game inspired by Kaun Banega Crorepati TV show.}
% \resumeItem{Infused Amitabh Bachchan's essence and voice into the project for an authentic experience.}
% \resumeItem{Integrated the Pygame library to enhance the gaming experience and designed checkpoints at specific questions to allow players to secure prize money.}
% \resumeItemListEnd


%-----------Achievements-----------
\section{Scholastic Achievements}
\resumeItemListStart
\resumeItem{Founded \textbf{\href{https://techbire.blogspot.com/}{TechBire}}, a tech blog, in 2017 and grew it into a monetized platform with 123 posts, implemented SEO strategies, and secured Google AdSense approval.}
\resumeItem{Produced quality and engaging tech content for \textbf{\href{https://m.dailyhunt.in/profile/techbire}{Dailyhunt}}, gaining over 7,000 followers in less than four months.}
\resumeItem{Selected as a Contributor for the GirlScript Summer of Code 2024 Program from among 30,000 registrations, placing in the \textbf{\href{https://www.linkedin.com/posts/techbire_ranked-under-top-300-among-30000-registrations-activity-7228989489681997827-F8pa?utm_source=share&utm_medium=member_desktop}{top 300}} on the leaderboard.}
\resumeItem{Participated in The Arcade 2023 \& 2024 by Google Cloud, winning a Standard tier swag prize.}
\resumeItem{Solved 100+ problems on \textbf{\href{https://leetcode.com/u/techbire/}{LeetCode}}, \textbf{\href{https://www.geeksforgeeks.org/user/techbire/}{GeeksforGeeks}}, and \textbf{\href{https://www.naukri.com/code360/profile/techbire}{Code360.}}}

\resumeItemListEnd
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: Python, C/C++, SQL, JavaScript, HTML/CSS} \\
\textbf{Frameworks and Libraries}{: React, Node.js, Streamlit, Pygame} \\
\textbf{Developer Tools and Platforms}{: Git, Docker, Google Cloud Platform, Figma, Canva, Firebase, Clerk} \\
}}
\end{itemize}

%-------------------------------------------
\end{document}
